---
title: "04 - Generalizability Assessment"
output: html_notebook
---
# Generalizability Assessment

This R notebook conducts an assessment on the generalizability of results of clinical
trials conducted using enrichment by comparing the demographic and clinical
characteristics of participants eligible under each selection criteria.


```{r}
library(tidyverse)
library(table1)
library(xtable)
```

Data manipulation to create a table 1 of baseline characteristics across eligible
participants. 

## Table 1 comparing each eligible cohort
```{r}
# filter for only baseline observations
baseline_unenriched<-unenriched_df%>%filter(visit==1)
baseline_capenriched<-capenriched_df%>%filter(visit==1)
baseline_pinenriched<-pinenriched_df%>%filter(visit==1)

# create composite dataframe
baseline_unenriched$cohort = 'Unenriched'
baseline_pinenriched$cohort = 'PIN'
baseline_capenriched$cohort = 'CAP'
baseline_df<-as.data.frame(rbind(baseline_unenriched,
                                 baseline_pinenriched,baseline_capenriched))
# data manupulation for table one creation
baseline_df$sex = ifelse(baseline_df$sex == 1, 'F','M')
baseline_df$Race = ifelse(baseline_df$race == 1, 'Caucasian','Non-Caucasian')
baseline_df$DCL = factor(baseline_df$DCL)

table1::label(baseline_df$age)<- "Age"
table1::label(baseline_df$sex)<- "Sex"
table1::label(baseline_df$TMS)<- "Baseline Total Motor Score (TMS)"
table1::label(baseline_df$SDMT)<- "Baseline Single Digit Modalities Test (SDMT)"
table1::label(baseline_df$TFCS)<- "Baseline Total Functional Capacity"
table1::label(baseline_df$DCL)<- "Baseline Diagnostic Confidence Level (DCL)"
table1::label(baseline_df$TMS)<- "Baseline Total Motor Score (TMS)"
table1::label(baseline_df$SWR)<- "Baseline Stroop Word Reading Test Score (SWR)"
table1::label(baseline_df$PIN)<- "Baseline PIN"
table1::label(baseline_df$CAP)<- "Baseline CAP"
table1::label(baseline_df$cuhdrs)<- "Baseline cUHDRS"
table1::label(baseline_df$cohort)<- "Subcohort"
```

```{r}
# function for custom presentation of each variable in the table one
# (ie mean vs median)
rndr <- function(x, name, ...) {
  if (!is.numeric(x)) return(render.categorical.default(x))
  what <- switch(name,
  age = "Mean (SD)",
  TMS = "Median [Q1,Q3]",
  SDMT = "Mean (SD)",
  TFC = "Median [Q1,Q3]",
  SWR = "Mean (SD)",
  PIN = "Mean (SD)",
  TFCS = "Median [Q1,Q3]",
  CAP = "Mean (SD)",
  cuhdrs = "Median [Q1,Q3]"
  )
  parse.abbrev.render.code(c("", what))(x)
}

# create table one
x<-table1(~ sex + age + Race + TMS + SDMT + TFCS + DCL + TMS + SWR + PIN + CAP + 
            cuhdrs | cohort, data = baseline_df,overall=F,render = rndr)
# print to latex format
xtable(as.data.frame(x))
```
```{r}
# display x
x
```

## Table 1 comparing eligible vs ineligible participants for each selection criteria

```{r}
baseline_unenriched<-baseline_df%>%filter(cohort=='Unenriched')
baseline_unenriched$CAP_eligible<-factor(ifelse(baseline_unenriched$CAP>cap.threshold,'Eligible','Not Eligible'))
baseline_unenriched$PIN_eligible<-factor(ifelse(baseline_unenriched$PIN>pin.threshold,'Eligible','Not Eligible'))

table(baseline_unenriched$CAP_eligible,baseline_unenriched$PIN_eligible)

table1::label(baseline_unenriched$age)<- "Age"
table1::label(baseline_unenriched$sex)<- "Sex"
table1::label(baseline_unenriched$TMS)<- "Baseline Total Motor Score (TMS)"
table1::label(baseline_unenriched$SDMT)<- "Baseline Single Digit Modalities Test (SDMT)"
table1::label(baseline_unenriched$TFCS)<- "Baseline Total Functional Capacity"
table1::label(baseline_unenriched$DCL)<- "Baseline Diagnostic Confidence Level (DCL)"
table1::label(baseline_unenriched$TMS)<- "Baseline Total Motor Score (TMS)"
table1::label(baseline_unenriched$SWR)<- "Baseline Stroop Word Reading Test Score (SWR)"
table1::label(baseline_unenriched$PIN)<- "Baseline PIN"
table1::label(baseline_unenriched$CAP)<- "Baseline CAP"
table1::label(baseline_unenriched$cuhdrs)<- "Baseline cUHDRS"
table1::label(baseline_unenriched$cohort)<- "Subcohort"
table1::label(baseline_unenriched$CAP_eligible)<- "Eligible for CAP group"
table1::label(baseline_unenriched$PIN_eligible)<- "Eligible for PIN group"

# create table one
y<-table1(~ sex + age + Race + TMS + SDMT + TFCS + DCL + TMS + SWR+ 
            cuhdrs | CAP_eligible, data = baseline_unenriched,overall=F,render = rndr)
# print to latex format
xtable(as.data.frame(y),booktabs=T)
y
```
```{r}
# create table one
y<-table1(~ sex + age + Race + TMS + SDMT + TFCS + DCL + TMS + SWR + 
            cuhdrs | PIN_eligible + CAP_eligible, data = baseline_unenriched,overall=F,render = rndr)
# print to latex format
xtable(as.data.frame(y))
y
```

